---
Title: "Implementing a Relational Database"
Course code: "CS5200"
Course: "Database Management Systems"
NUID:"002647248"
---
The first step in using sqlite in R Studio is to determine whether the "RSQLite" package is already installed. If not, install it. 
To use the functions, import "RSQLite," and then connect to the database or other location where the actions will be carried out. If the file hasn't already been created, a new file will be generated.
The specified path has been used to build a database called prosql.db, and tables are presently being created there

```{r}
library("RSQLite")
fpath="C:/Users/welcome/Downloads/"
dbfile="prosql.db"
dbcon1<- dbConnect(RSQLite::SQLite(),paste0(fpath,dbfile))

```

pragma foreign_keys = on enforces foreign keys. This is usually necessary because by default, SQLite does not enforce foreign keys.you could use R chunk or sql chunk to enable pragma. 

```{r}
dbExecute(dbcon1, "PRAGMA foreign_keys = ON")
```
Writing conditions to drop a table if the table already exists.

```{sql connection=dbcon1}
DROP TABLE IF EXISTS ModuleAuthorTracker
```

```{sql connection=dbcon1}
DROP TABLE IF EXISTS Module
```

```{sql connection=dbcon1}
DROP TABLE IF EXISTS Author
```

```{sql connection=dbcon1}
DROP TABLE IF EXISTS Affiliation
```

establishing a module-named table. Given that the term "number" is a reserved key word, it is not ideal for one of the attributes with the name "number" to have the same name. As a result, we changed number to "m number" and added other attributes as well. 


```{sql connection=dbcon1}
CREATE TABLE Module(
m_number TEXT PRIMARY KEY NOT NULL, 
title  TEXT NOT NULL,
lengthinMin INTEGER NOT NULL)
```

establishing a Author named table with the required attributes

```{sql connection=dbcon1}
CREATE TABLE Author(
aid INTEGER PRIMARY KEY NOT NULL,
name TEXT NOT NULL,
email TEXT NOT NULL,
affid INTEGER NOT NULL,
FOREIGN KEY(affid) REFERENCES Affiliation(affid)
)
```

establishing a Affiliation named lookup table with the required attributes

```{sql connection=dbcon1}
CREATE TABLE Affiliation(
affid INTEGER PRIMARY KEY NOT NULL,
affiliation TEXT NOT NULL
)
```

The module and author tables has zero-many and many-many relationships and to decompose that we had a junction table hence we created a junction table named ModuleAuthorTracker having m_number and aid as both primary keys and foriegn keys.

```{sql connection=dbcon1}
CREATE TABLE ModuleAuthorTracker
(
m_number TEXT,
aid INTEGER,
PRIMARY KEY(m_number,aid),
FOREIGN KEY(aid) REFERENCES Author(aid),
FOREIGN KEY(m_number) REFERENCES Module(m_number)
)

```

Inserting values into Module table

```{sql connection=dbcon1}
INSERT INTO Module VALUES
("a","Harrypotter",200),
("b","Saregama",300),
("c","dramatic",400)
```

Retrieving Data from Module table

```{sql connection=dbcon1}
select * from Module
```
Inserting values into Affiliation table

```{sql connection=dbcon1}
INSERT INTO Affiliation VALUES
(11,"PT"),
(22,"FT"),
(33,"Contract")

```

retrieving data from Affiliaiton table

```{sql connection=dbcon1}
select * from Affiliation
```

Inserting values into Author table

```{sql connection=dbcon1}
INSERT INTO Author VALUES
(1,"jayantha","dara.j@gmail.com",11),
(2,"jayatha","akuluri@gmail.com",22),
(3,"jayan","nanduri.j@gmail.com",33),
(4,"jayani","jayani@gmail.com",33)
```

Data retrieving from Author table

```{sql connection=dbcon1}
select * from Author
```

Inserting values into ModuleAuthorTracker table

```{sql connection=dbcon1}
INSERT INTO ModuleAuthorTracker(aid,m_number) VALUES
(1,"a"),
(1,"b"),
(1,"c"),
(2,"b"),
(3,"c")

```

Retriving data from ModuleAuthorTracker table

```{sql connection=dbcon1}
select * from ModuleAuthorTracker
```
Retriving Title,author and affiliation data from all the tables in database

```{sql connection=dbcon1}
select Module.title,Author.name,Affiliation.affiliation from Module 
inner join ModuleAuthorTracker on Module.m_number=ModuleAuthorTracker.m_number
inner join Author on Author.aid=ModuleAuthorTracker.aid
inner join affiliation on Affiliation.affid=Author.affid

```
disconnect the database by using dbDisconnect command

```{r}
dbDisconnect(dbcon1)
```

