---
title: "Store XML in a Database"
author: "Gowreesh Gunupati"
date: "2023-04-05"
output: html_document
---

## R Markdown

## Question 1:
```{r}
library(imager)
link <- "http://imgur.com/vUxIAjj.jpeg"
knitr::include_graphics(link)
```
```{r}
library(XML)
library(sqldf)
```

## Question 2:
```{r}
#load RSQLite package

library(RSQLite)


fpath = ""
dbfile = "myDB.sqlite"

# if database file already exists, connect to it, otherwise
#create a new database
dbcon <- dbConnect(RSQLite::SQLite(), paste0(fpath,dbfile))

```

### Enable Foreign Key Constraint.
```{r} 
dbExecute(dbcon, "PRAGMA foreign_keys = ON")
```

### Drop tables if they exist.
```{sql connection=dbcon}
DROP TABLE IF EXISTS Book
```

```{sql connection=dbcon}
DROP TABLE IF EXISTS Author
```

```{sql connection=dbcon}
DROP TABLE IF EXISTS Genre
```

### Create tables in the database.
```{sql connection=dbcon}
CREATE TABLE Author(
  aid NUMBER NOT NULL,
  name TEXT NOT NULL,
  PRIMARY KEY (aid)
);
```


```{sql connection=dbcon}
CREATE TABLE Genre(
  gid NUMBER NOT NULL,
  genrename TEXT NOT NULL,
  PRIMARY KEY (gid)
);
```

```{sql connection=dbcon}
CREATE TABLE Book(
  id TEXT NOT NULL,
  title TEXT NOT NULL,
  price DOUBLE NOT NULL,
  pubdate DATE NOT NULL,
  description TEXT NOT NULL,
  edition number,
  aid NUMBER NOT NULL,
  gid NUMBER NOT NULL,
  FOREIGN KEY (aid) REFERENCES Author(aid),
  FOREIGN KEY (gid) REFERENCES Genre(gid),
  PRIMARY KEY (id)
);
```

```{sql connection=dbcon}
SELECT * FROM Author
```

```{sql connection=dbcon}
SELECT * FROM Genre
```

```{sql connection=dbcon}
SELECT * FROM Book
```
## Question 3:
```{r}
library(XML)

xmlFile <- "Books-v3.xml"

dom <- xmlParse(xmlFile)

# get the root node of the DOM tree
r <- xmlRoot(dom)

numberofBooks <- xmlSize(r)
```

Creating dataframes and loading data into tables in database.

```{r}
Books<-xmlToDataFrame(dom)

Books$description<-gsub("\n","", Books$description)

Books$price<-as.double(Books$price)

Books$publish_date<-as.Date(Books$publish_date)

Books$edition<-as.integer(Books$edition)

Books$id<-1:nrow(Books)


Books
```

creating a dataframe for genres DataFrame


```{r}
genres<-data.frame(name=unique(Books$genre))
genres$gid<-1:nrow(genres)
genres
```

```{r}
Authors<-data.frame(name=unique(Books$author))
Authors$aid<-1:nrow(Authors)
Authors
```

```{r}
query <- "INSERT INTO Author (aid, name ) VALUES"

# Finish it with
query <- paste(query, paste(sprintf('("%s", "%s")', Authors$aid, Authors$name), collapse = ","))
```

```{r}
rs <- dbSendQuery(dbcon,query)
dbClearResult(rs)
```

```{r}
query <- "insert into Genre (gid, genrename ) VALUES"

# Finish it with
query <- paste(query, paste(sprintf('("%s", "%s")', genres$gid, genres$name), collapse = ","))
```

```{r}
rs <- dbSendQuery(dbcon,query)
dbClearResult(rs)
```

```{r}
s<-sqldf("select Authors.aid from Authors join Books on Books.author=Authors.name")
Books$aid<-s$aid
g<-sqldf("select genres.gid from genres join Books on Books.genre=genres.name")
Books$gid<-g$gid
```


```{r}
query <- "insert into Book (id, title, price, pubdate, description,edition, aid, gid ) VALUES"

# Finish it with
query <- paste(query, paste(sprintf('("%s", "%s", "%s", "%s", "%s", "%s","%s","%s")', Books$id, Books$title, Books$price, Books$publish_date, Books$description,Books$edition, Books$aid, Books$gid), collapse = ","))
```

```{r}
rs <- dbSendQuery(dbcon,query)
dbClearResult(rs)
```

```{sql connection=dbcon}
SELECT * FROM BOOK
```

### Displaying data loaded into the database form the XML.
```{sql connection=dbcon}
Select * from Book
```

```{sql connection=dbcon}
Select * from Author
```

```{sql connection=dbcon}
Select * from Genre
```

## Question 5:A
```{sql connection=dbcon}
SELECT COUNT(gid) as numOfGenres FROM (SELECT gid FROM Book GROUP BY gid HAVING COUNT(gid)>=3)
```

## Question 5:B
```{sql connection=dbcon}
SELECT strftime('%Y' , pubdate) as oldestYear from Book
ORDER BY pubdate ASC
LIMIT 1
```


## Question 5:C
```{sql connection=dbcon}
SELECT g.genrename, count(*) as numOfBooks, avg(price) from Book as b
INNER JOIN Genre as g ON b.gid = g.gid
GROUP BY g.gid
```

## Question 5:D
```{sql connection=dbcon}
SELECT b.title, a.name from Book as b INNER JOIN Author as a 
ON b.aid = a.aid where b.price < 0.8 * (select avg(price) from Book) or
b.price > 1.2* (select avg(price) from Book)
```

# Disconnect from Database after the program to free up database and other resources.
```{r}
dbDisconnect(dbcon)
```
